---
title: "Lab 3 Report"
author: "Amara Miller"
date: "`r format(Sys.Date())`"
output: github_document
---

Instructions for this lab report can be found on [Your assignment section of Lab Assignment 3 Introduction to ggplot2](https://biol275-msum.github.io/introduction-to-ggplot2.html#your-assignment) on the lab website.

## Fireflies

> A. Insert an R code chunk and create a graph depicting the frequency distribution of the 35 mass measurements. It should have legible text and appropriate axis labels.

```{r}
# Load packages -----------------------------------------------------------

library(tidyverse)

# Spermatophore mass in male fireflies -------------------------------------

firefly_data <- read_csv("https://whitlockschluter.zoology.ubc.ca/wp-content/data/chapter02/chap02q19FireflySpermatophoreMass.csv")


ggplot(data = firefly_data) +
  geom_histogram(mapping = aes(x = spermatophoreMass), bins = 14,
                 boundary = 0, closed = "left", 
                 fill = "#C5351B", color = "black") +
  labs(x = "Spermatophore Mass (kg)", y = "Frequency (number of species)") +
  scale_y_continuous(breaks = seq(0, 15, 5), limits = c(0, 15), 
                     expand = expansion(mult = 0)) +
  scale_x_continuous(breaks = seq(0, 0.2, 0.02)) +
  theme_classic() +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black", size = rel(1))
  )
```


> B. What type of graph did you choose in part (A)? Why?

I chose to make a histogram in part (A). A histogram displays the frequency distribution of a numerical variable. 

> C. Describe the shape of the frequency distribution. What are its main features?

The histogram seems to have a sort of bell shape with one outlier on the right. It looks like it is unimodel also. 

> D. What term would be used to describe the largest measurement in the frequency distribution? You can refer to the lecture slides, your notes, or the textbook.

The largest measurement in the frequency distribution is the mode. 


## Bird orders

I read the data using the code provided by the instructor. The dataset is from the auk package and was originally named ebird_taxonomy. I converted it to a tibble, removed non-species taxa, and named the new dataset birds.

```{r}
library(auk)                          # load the auk package
birds <- ebird_taxonomy %>%           # start with the ebird_taxonomy data
  as_tibble() %>%                     # tibbles print better in the console
  filter(category == "species")       # remove non-species taxa
```

> E. How many bird species are in the new birds dataset? How did you find out?

There are 10,721 bird species in the new birds dataset. I looked at the birds data and did a count on the scientific name and saw that there were 10,721 rows of data.

> H. How many orders are there? You can get this right by counting on the graph, but you will only get full points if you use some code to figure it out.

I used the code, count(birds, order), to determine that there are 41 different orders after I noticed that there are 41 rows of data. 

> F. Insert an R code chunk and create a graph depicting the distribution of orders in the birds dataset. Sort the orders with the most frequent on the left. It should have legible text and appropriate axis labels.

```{r}
birds

ggplot(data = birds) +
  geom_bar(mapping = aes(x = fct_rev(fct_infreq(order))), fill = "#C5351B", 
           width = .8) +
  labs(x = "Order", y = "Frequency (number of species)") +
  scale_y_continuous(limits = c(0, 6500), expand = expansion(mult = 0)) +
  coord_flip() +
  theme_classic(base_size = 12) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black", size = rel(0.6)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.ticks.x = element_blank()
  )

```

> G. What kind of graph did you create? Why?

I created a bar chart because the order of birds represents a categorical value and that is best shown with a bar chart. 

## Links to peer review

I reviewed MaryJo Nelson's lab report at this URL: https://github.com/BIOL275-MSUM/lab-3-intro-to-ggplot-MaryJo-Nelson

MaryJo Nelson reviewed my lab report at this URL: https://github.com/BIOL275-MSUM/lab-3-intro-to-ggplot-milleramara4

## Session Info

Here is my session information:

```{r}
sessioninfo::session_info()
```